Viscous Erosion in Porous Media

### 2018-02-26 docs/methods/erosion_methods.tex
Modified codes for convergence test to output CPU time too.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.75 \textwidth]{./figs/shrink_intface.pdf}
\caption{
Shape and stress evolution. (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals. Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes. (b) The distribution of absolute shear stress, $\atau$, along each of these interfaces. Normalized arc length, $s/L$, runs counterclockwise from the rear stagnation point. The stress initially varies over the body's surface, but becomes more uniform over time.}
\label{shrink_intface}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/fixed_intface.pdf}
\caption{One body fixed area}
\label{fixed_intface}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024c5
% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0

@@

As a final validation, we now aim to verify the second-order temporal convergence rate of our method. To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} to a stopping time of $t_s = 1E-2$, which is 56\% of the time it takes for the body to vanish completely. By this time, the body has eroded substantially, but is not so small that accuracy is lost. We assess error by measuring the difference between simulations of successive temporal resolution (i.e.~we verify Cauchy convergence). In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time, $t_s$, while successively halving the timestep $\Delta t$. Table \ref{convtab} shows the $L^2$-errors between successive simulations, along with the order of accuracy as obtained by Richardson-extrapolation-type calculations. The table confirms that our method to converges with second-order accuracy.

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Convergence test: we run erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$ difference in shapes obtained with successive temporal resolution. The tests confirm the method to be second-order accurate in time.
}
\vspace{0.3 pc}
\label{convtab}
\begin{tabular}{c l l}
\hline
\hspace{0.5pc} $\Delta t/t_s$
\hspace{0.5pc} & error 
\hspace{0.5pc} & order \\
\hline
%
1/50		& 1.68E-5		& --		\\
1/100	& 4.84E-6		& 1.79	\\
1/200	& 1.30E-6		& 1.90	\\
1/400	& 3.36E-7		& 1.95	\\
1/800	& 8.54E-8		& 1.98	\\
1/1600	& 2.15E-8		& 1.99	\\
1/3200	& 5.40E-9		& 1.99	\\
1/6400	& --			& --		\\
%
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Parameters in this test are: 01circ256, nits = 7, dt0 = 1e-4, tfin = 1e-2
% epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 0

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.75 \textwidth]{./figs/shrink_intface.pdf}
\caption{
Shape and stress evolution: (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals. Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes. (b) The distribution of absolute shear stress, $\atau$, along each of these interfaces. Normalized arc length, $s/L$, runs counterclockwise from the rear stagnation point. The stress initially varies over the body's surface, but becomes more uniform over time.}
\label{shrink_intface}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/fixed_intface.pdf}
\caption{Fixed-area simulations: (a) Interfaces of a body eroding under shear stress but with the area artifically kept constant. Inset: zoom near the rear stagnation point, showing that the corner is actually smooth on a fine scale. (b) The stress distribution on the surface of the body. Over time, the stress becomes more uniform.}
\label{fixed_intface}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024c5
% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0

@@

As a final validation, we now aim to verify the second-order temporal convergence rate of our method. To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with $N_\iin=128$) to a stopping time of $t_s = 1E-2$. This stopping time is 56\% of the time it takes for the body to vanish completely, so that the body has eroded substantially, but is not so small that accuracy is lost. We assess error by measuring the difference between simulations of successive temporal resolution (i.e.~we verify Cauchy convergence). In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time, $t_s$, while successively halving the timestep $\Delta t$. Table \ref{convtab} shows the $L^2$-errors between successive simulations, along with the order of accuracy as obtained by Richardson-extrapolation-type calculations. The table confirms that our method to converges with second-order accuracy.

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Convergence test: We run erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$ difference in shapes obtained with successive temporal resolution. The tests confirm the method to be second-order accurate in time.
}
\vspace{0.3 pc}
\label{convtab}
\begin{tabular}{l l l l}
\hline
\hspace{0.0pc} $\Delta t/t_s$
\hspace{0.5pc} & error 
\hspace{0.5pc} & order
\hspace{0.5pc} & CPU time \\
\hline
%
1/50		& 1.68E-5		& --		& 55 secs		\\
1/100	& 4.84E-6		& 1.79	& 1.8 mins		\\
1/200	& 1.30E-6		& 1.90	&	\\
1/400	& 3.36E-7		& 1.95	&	\\
1/800	& 8.54E-8		& 1.98	&	\\
1/1600	& 2.15E-8		& 1.99	&	\\
1/3200	& 5.40E-9		& 1.99	&	\\
1/6400	& --			& --		&	\\
%
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Parameters in this test are: 01circ256, nits = 7, dt0 = 1e-4, tfin = 1e-2
% epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 0
